Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-06-25 ms.tex
added transformed versions of first eigenvectors.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
The first two principal components (Right) do not isolate any separate populations of transits.
As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
\end{centering}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255_transformed.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Top Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
The first two principal components (Bottom) do not isolate any separate populations of transits.
As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
\end{centering}
\end{figure*}
